Brouillon PoF,PRF..

### 2019-01-07 draft_p2.tex
Ajoute un paragraphe d'intro pour la section sur l'échantillonnage direct des fluctuations de trainée

\begin{document}
\title{A statistical mechanics approach to the simulation of extreme fluctuations of the time-averaged drag acting on an obstacle immersed in a turbulent flow}

@@

\paragraph*{Paragraphe d'introduction: les motivations d'un étude directe ?}
%% TODO: Introduire la notion de temps de retour
Rare event algorithms relies on the simulation of an ensemble of trajectories.
Members of the ensemble can be duplicated or removed from the ensemble, based on the evaluation of a \textit{score function}.
A score function is an observable of the trajectories that can quantify how interesting is a trajectory with respect to the realisation of a rare event.
For instance, if one is interested in a rare transition between two region of phase space, a possible choice for the score function is the minimal distance to the target set achieved by the trajectory.
In cases where one is interested in computing rare trajectories over which a given observable reaches a fixed threshold, an obvious score function is the maximum value of the observable over the trajectory.
However, for high-dimensional dynamics with a very complex phase space, the simple distance to the target event is likely to be a very poor criterion for selecting rare trajectories.
\textbf{[...]}

\subsection{Extracting extreme drag fluctuations from a very long timeseries}
\label{sec:extreme_extraction}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{return_time_drag}
  \caption{Drag fluctuation amplitude as a function the corresponding return time. The return time $r(a)$ is the typical timescale of occurrence of a fluctuation of amplitude larger than $a$.}
  \label{fig:return_time_instant}
\end{figure}
\subsection{Instantaneous drag}
\label{sec:instantaneous_drag}

@@

%% Limites de l'approche par échantillonnage direct
In the limit of very rare events and/or very complex dynamics such as turbulent flows in industrial contexts, a direct sampling approach is unrealistic.
For instance, in the limit of extreme positive fluctuations, the return time of a fluctuations $f_d \geq a$ verifies~\ref{sec:lestang2018}
\begin{equation}
  \label{eq:return_time_scaling}
  r(a) \underset{a\to\infty}{\propto} \frac{1}{\mathbb{P}(f_d\geq a)} \propto e^{\alpha a}
\end{equation}
where $\alpha$ is the rate describing the positive tail of the drag \ac{pdf}, see figure~\ref{fig:pdf_drag}.
As a result, the computational cost required to sample events $f_d \geq a$ scales like $e^{\alpha a}$.

>>>>

\begin{document}
\title{Brouillon PoF,PRF..}

@@

In this section we describe the phenomenology of extreme fluctuations of the drag that acts on the square cylinder mounted in the flow described in section~\ref{sec:test_flow}.

How rare is a fluctuation $f_d \geq a$ can be determined by computing its \textit{return time} $r(a)$.
It is defined as the average time between two consecutive occurrences of a fluctuation $f_d \geq a$.
Extreme drag fluctuations are \textit{rare events}, that is fluctuations for which $r(a) \gg \tau_c$.
In this context, the occurrence of the fluctuations follows a Poisson process and~\cite{lestang2018}
\begin{equation}
  \label{eq:return_time}
  r(a) \underset{a\to\infty}{\propto} \frac{1}{\mathbb{P}(f_d\geq a)} \propto e^{\alpha a}
\end{equation}
where $\alpha$ is the rate describing the positive tail of the drag \ac{pdf}, see figure~\ref{fig:pdf_drag}.
Figure~\ref{fig:return_time_instant} illustrates the fluctuation amplitude $a$ as a function of the return time $r(a)$, for the drag process $f_d(t)$.
Such plot can be obtained from a sample timeseries following a simple procedure~\cite{lestang2018}.

In the following we discuss extreme fluctuations of both the instantaneous drag $f_d$ and time-averaged drag with return times larger than $10^4\tau_c$.
In this section extreme drag fluctuations are simply sampled by simulating the flow over a very long duration.
This approach is referred to as \textit{direct sampling}, as opposed to approaches involving the use of rare events algorithms, discussed in section~\ref{sec:rare_events_algorithms}.
Such approach is made possible by the relative simplicity of the flow described in section~\ref{sec:test_flow}.
The control run mentioned in the previous section, spanning $T_{tot} = 10^6 \tau_c$, could be achieved in a wall-clock time of a few weeks and gives access to extreme fluctuations $f_d \geq a$ with a return time $r(a) \leq 10^6\tau_c$.
\subsection{Extracting extreme drag fluctuations from a very long timeseries}
\label{sec:extreme_extraction}

@@

\begin{figure}
  \centering
  \includegraphics[width=.6\linewidth]{return_time_drag}
  \caption{Drag fluctuation amplitude as a function the corresponding return time. The return time $r(a)$ is the typical timescale of occurrence of a fluctuation of amplitude larger than $a$.}
  \label{fig:return_time_instant}
\end{figure}
\subsection{Instantaneous drag}
\label{sec:instantaneous_drag}

@@

%% Limites de l'approche par échantillonnage direct
In the limit of very rare events and/or very complex dynamics such as turbulent flows in industrial contexts, a direct sampling approach is unrealistic.
Indeed, according to equation~\eqref{eq:return_time_scaling}, the return time of a fluctuation $f_d \geq a$ verifies $r(a) \propto e^{\alpha a}$.
As a result, the computational cost required to sample events $f_d \geq a$ scales like $e^{\alpha a}$.
